Assessment of drought impact over land cover in continental Chile by the analysis of water supply and demand from ERA5-Land and MODIS

### 2024-01-11 article/paper_drought_Chile2023.qmd
completar area de estudio en articulo

>>>>

Continetal Chile has a diverse climate condition from north to south and east to west, which determines its great ecosystem diversity [@Aceituno2021]. The Andes Mountains are a main factor in longitudinal variation [@Garreaud2009]. Acoording to the v2 of the Koppen-Geiger realease by @Beck2023 and the landcover types from the IGBP [@Friedl2019]. In the "Norte Grande" and "Norte Chico" predominate an arid desert climate with hot (Bwh) and cold (Bwk) temperatures. At south of "Norte Chico" the climate change to a arid steppe with cold temperatures (Bsk). Mainly the land is barrend and with a minor surface of vegetation types of Shrubland (X% ) and Grassland.

### 2024-01-11 article/paper_drought_Chile2023.tex
completar area de estudio en articulo

\begin{keyword}
    drought \sep land cover change \sep 
    satellite
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

>>>>

\begin{keyword}
    drought \sep land cover change \sep 
    satellite
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Continetal Chile has a diverse climate condition from north to south and
east to west, which determines its great ecosystem diversity
\citep{Aceituno2021}. The Andes Mountains are a main factor in
longitudinal variation \citep{Garreaud2009}. Acoording to the v2 of the
Koppen-Geiger realease by \citep{Beck2023} and the landcover types from
the IGBP \citep{Friedl2019}. In the ``Norte Grande'' and ``Norte Chico''
predominate an arid desert climate with hot (Bwh) and cold (Bwk)
temperatures. At south of ``Norte Chico'' the climate change to a arid
steppe with cold temperatures (Bsk). Mainly the land is barrend and with
a minor surface of vegetation types of Shrubland (X\% ) and Grassland.
